### 2020-10-10 Thesis-Chapter3-Arguments.tex
Add signal x3dh protocol DFD
Add OODA loop diagram and notes; update outline

Wicked problems

@@

% Mention hermeneutics and complex adaptive systems?

@@

@@

@@

feeley_judicial_2000:
- Classical analytic method ("linear" in commission_tackling_2018)
- Incremental intuitive decision making ("Muddling through" in rozenshtein_wicked_2018)
- The hermeneutic circle

>>>>

Wicked problems. \ac{OODAloop}.

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-loop.png}
    \caption[The OODA Loop]{The OODA Loop}
    \label{fig-ooda-loop}
\end{figure}

@@

% Mention hermeneutics and complex adaptive systems?
% As feeley_judicial_2000 points out, muddling through is too focused on, or even consists entirely of, the
% implementation step. Because of the long tail effects of any implementation in a wicked scenario, and especially in
% the context of encryption, mere muddling through is too risky. Therefore I suggest iteration. Classical methods, but
% applied in a cyclical manner.

@@

% See committee_decrypting_2018!
% For a wholistic threat model, include both the threats of government (legislation) and of criminal abusers of your
% system.

@@

% See committee_decrypting_2018!

@@

feeley_judicial_2000:
- Classical analytic method ("linear" in commission_tackling_2018)
% 1. Classical analytic method; each step has its own approaches, e.g. cost-benefit analysis (loosely based on natural
% sciences)
%   (missing: Observe)
%   a. Define the problem (Orient)
%   b. Identify a goal (Orient)
%   c. Generate a range of alternatives for achieving that goal (Orient)
%   d. Select the alternative that seems most promising (Decide)
%   e. Implement the selected alternative (Act)
%   (missing: loop)
- Incremental intuitive decision making ("Muddling through" in rozenshtein_wicked_2018)
- The hermeneutic circle
